---
title: "Wicket Gate Replacement Economic Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: WhiteTransparentLogo-small.png
    theme: spacelab
    css: styles.css
runtime: shiny
---

```{r setup, include=FALSE}

library(flexdashboard)

source("Functions.R")

# Default values
{
  # Costs incurred for other projects at time 0
  sunk.cost.labor.default <- c(2500, 3500, 4500)
  sunk.cost.outage.default <- c(315, 924, 1927.8)
  
  
  # Refurbish
  wg.refurb.life.default <- c(15,30,45)
  wg.refurb.cost.materials.default <- c(500, 800, 3000)
  wg.refurb.cost.labor.default <- c(2500, 3500, 4500)
  wg.refurb.cost.outage.default <- c(315, 924, 1927.8)
  
  
  # New
  wg.replace.life.default <- c(100, 100, 100)
  wg.replace.cost.materials.default <- c(1800, 2200, 3000)
  wg.replace.cost.labor.default <- c(2500, 3500, 4500)
  wg.replace.cost.outage.default <- c(315, 924, 1927.8)
  
  
  n.default <- 10000
  rate.discount.default <- .044
  n.units.default <- 7
}



```

Selections {.sidebar data-width=350}
=====================================

***

```{r input_run}

actionButton("run.simulation", label = "Run simulation")

```

***

```{r input_reset}

actionButton("reset", label = "Reset values to default")

observeEvent(
  input$reset,
  {
    # Refurb
      updateSliderInput(
        inputId = "refurb.cost.labor.bounds", 
        value = wg.refurb.cost.labor.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "refurb.cost.labor.ev",
        value = wg.refurb.cost.labor.default[2]
      )
      updateSliderInput(
        inputId = "refurb.cost.materials.bounds", 
        value = wg.refurb.cost.materials.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "refurb.cost.materials.ev",
        value = wg.refurb.cost.materials.default[2]
      )
      updateSliderInput(
        inputId = "refurb.cost.outage.bounds", 
        value = wg.refurb.cost.outage.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "refurb.cost.outage.ev",
        value = wg.refurb.cost.outage.default[2]
      )
      updateSliderInput(
        inputId = "refurb.life.bounds", 
        value = wg.refurb.life.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "refurb.life.ev",
        value = wg.refurb.life.default[2]
      )
      
    # Replace
      updateSliderInput(
        inputId = "replace.cost.labor.bounds", 
        value = wg.replace.cost.labor.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "replace.cost.labor.ev",
        value = wg.replace.cost.labor.default[2]
      )
      updateSliderInput(
        inputId = "replace.cost.materials.bounds", 
        value = wg.replace.cost.materials.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "replace.cost.materials.ev",
        value = wg.replace.cost.materials.default[2]
      )
      updateSliderInput(
        inputId = "replace.cost.outage.bounds", 
        value = wg.replace.cost.outage.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "replace.cost.outage.ev",
        value = wg.replace.cost.outage.default[2]
      )
      updateSliderInput(
        inputId = "replace.life.bounds", 
        value = wg.replace.life.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "replace.life.ev",
        value = wg.replace.life.default[2]
      )
    
    # Other
      updateSliderInput(inputId = "rate.discount", value = rate.discount.default*100)
      updateSliderInput(
        inputId = "sunk.cost.labor.bounds", 
        value = sunk.cost.labor.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "sunk.cost.labor.ev",
        value = sunk.cost.labor.default[2]
      )
      updateSliderInput(
        inputId = "sunk.cost.outage.bounds", 
        value = sunk.cost.outage.default[c(1,3)]
      )
      updateNumericInput(
        inputId = "sunk.cost.outage.ev",
        value = sunk.cost.outage.default[2]
      )
      updateSliderInput(inputId = "n", value = n.default)
      updateSliderInput(inputId = "n.units", value = n.units.default)
  }
)


```


***

Cost inputs in thousands of dollars.

***


### **Refurbish Inputs:**

##### *Materials*

```{r}
# Materials
  sliderInput(
    "refurb.cost.materials.bounds", "Cost Bounds:",  
    min = 0, 
    value = c(wg.refurb.cost.materials.default[1], wg.refurb.cost.materials.default[3]),
    max = 5000, 
    step = 50
  )
  
  numericInput(
    "refurb.cost.materials.ev",
    "Cost Expected Value:",
    value = wg.refurb.cost.materials.default[2], 
    step = 50
  )
```

***

<!-- ##### *Labor* -->

```{r eval=FALSE, include=FALSE}
# Labor
  sliderInput(
      "refurb.cost.labor.bounds", "Cost Bounds:",  
      min = 0, 
      value = c(wg.refurb.cost.labor.default[1], wg.refurb.cost.labor.default[3]),
      max = 6000, 
      step = 50
    )
    
  numericInput(
    "refurb.cost.labor.ev",
    "Cost Expected Value:",
    value = wg.refurb.cost.labor.default[2], 
    step = 100
  )
```

<!-- *** -->

<!-- ##### *Outage* -->

```{r eval=FALSE, include=FALSE}
# Outage
  sliderInput(
    "refurb.cost.outage.bounds", "Cost Bounds:",  
    min = 0, 
    value = c(wg.refurb.cost.outage.default[1],wg.refurb.cost.outage.default[3]),
    max = 1000, 
    step = 25
  )
  
  numericInput(
    "refurb.cost.outage.ev",
    "Cost Expected Value:",
    value = wg.refurb.cost.outage.default[2],
    step = 50
  )
```

<!-- *** -->

##### *Life*

```{r}
# Life
  sliderInput(
    "refurb.life.bounds", "Life Bounds:",  
    min = 0, 
    value = c(wg.refurb.life.default[1], wg.refurb.life.default[3]),
    max = 100, 
    step = 1
  )
  
  numericInput(
    "refurb.life.ev",
    "Life Expected Value:",
    value = wg.refurb.life.default[2],
    step = 1
  )
```

***

### **Replace Inputs:**

##### *Materials*

```{r}

# Materials
  sliderInput(
    "replace.cost.materials.bounds", "Cost Bounds:",  
    min = 0, 
    value = c(wg.replace.cost.materials.default[1], wg.replace.cost.materials.default[3]),
    max = 5000, 
    step = 50
  )
  
  numericInput(
    "replace.cost.materials.ev",
    "Cost Expected Value:",
    value = wg.replace.cost.materials.default[2], 
    step = 100
  )


```

***

##### *Labor (Future)*

```{r}

# Labor
  sliderInput(
      "replace.cost.labor.bounds", "Cost Bounds:",  
      min = 0, 
      value = c(wg.replace.cost.labor.default[1], wg.replace.cost.labor.default[3]),
      max = 6000, 
      step = 50
    )
    
  numericInput(
    "replace.cost.labor.ev",
    "Cost Expected Value:",
    value = wg.replace.cost.labor.default[2], 
    step = 100
  )
  
```

***

##### *Outage (Future)*

```{r}

# Outage
  sliderInput(
    "replace.cost.outage.bounds", "Cost Bounds:",  
    min = 0, 
    value = c(wg.replace.cost.outage.default[1],wg.replace.cost.outage.default[3]),
    max = 3000, 
    step = 25
  )
  
  numericInput(
    "replace.cost.outage.ev",
    "Cost Expected Value:",
    value = wg.replace.cost.outage.default[2],
    step = 50
  )
  
```

***

##### *Life*

```{r}

# Life
  sliderInput(
    "replace.life.bounds", "Life Bounds:",  
    min = 50, 
    value = c(wg.replace.life.default[1], wg.replace.life.default[3]),
    max = 200, 
    step = 1
  )
  
  numericInput(
    "replace.life.ev",
    "Life Expected Value:",
    value = wg.replace.life.default[2],
    step = 5
  )

```

***


### **Other:**

<!-- ##### *Sunk Labor* -->

```{r eval=FALSE, include=FALSE}

# Labor
  sliderInput(
      "sunk.cost.labor.bounds", "Cost Bounds:",  
      min = 0, 
      value = c(sunk.cost.labor.default[1], sunk.cost.labor.default[3]),
      max = 6000, 
      step = 50
    )
    
  numericInput(
    "sunk.cost.labor.ev",
    "Cost Expected Value:",
    value = sunk.cost.labor.default[2], 
    step = 100
  )
  
```

<!-- ##### *Sunk Outage* -->

```{r eval=FALSE, include=FALSE}

# OUtage
  sliderInput(
    "sunk.cost.outage.bounds", "Cost Bounds:",  
    min = 0, 
    value = c(sunk.cost.outage.default[1], sunk.cost.outage.default[3]),
    max = 1000, 
    step = 25
  )
  
  numericInput(
    "sunk.cost.outage.ev",
    "Cost Expected Value:",
    value = sunk.cost.outage.default[2], 
    step = 50
  )


```

#### *Simulation Variables*

```{r}

sliderInput(
  "n", "Simulation Size:",  
  min = 1000, 
  value = n.default,
  max = 100000, 
  step = 500
)

sliderInput(
  "n.units", "Number of Units:",  
  min = 1, 
  value = n.units.default,
  max = 7, 
  step = 1
)

sliderInput(
  "rate.discount", "Discount Rate:",  
  min = 0, 
  value = rate.discount.default*100,
  max = .2*100, 
  step = .001*100,
  post = "%"
)

```


***

```{r define_vars}

# Sunk
  sunk.cost.labor <- reactive({c(
    input$sunk.cost.labor.bounds[1],
    input$sunk.cost.labor.ev,
    input$sunk.cost.labor.bounds[2]
  )*1000})
  
  sunk.cost.outage <- reactive({c(
    input$sunk.cost.outage.bounds[1],
    input$sunk.cost.outage.ev,
    input$sunk.cost.outage.bounds[2]
  )*1000})

# Other
  n <- reactive({input$n})
  n.units <- reactive({input$n.units})
  rate.discount <- reactive({input$rate.discount/100})

# Refurb
  refurb.cost.materials <- reactive({c(
    input$refurb.cost.materials.bounds[1],
    input$refurb.cost.materials.ev,
    input$refurb.cost.materials.bounds[2]
  )*1000})
  
  refurb.cost.labor <- reactive({c(
    input$refurb.cost.labor.bounds[1],
    input$refurb.cost.labor.ev,
    input$refurb.cost.labor.bounds[2]
  )*1000})
  
  refurb.cost.outage <- reactive({c(
    input$refurb.cost.outage.bounds[1],
    input$refurb.cost.outage.ev,
    input$refurb.cost.outage.bounds[2]
  )*1000})
  
  refurb.life <- reactive({c(
    input$refurb.life.bounds[1],
    input$refurb.life.ev,
    input$refurb.life.bounds[2]
  )})

# Replace
  new.cost.materials <- reactive({c(
    input$replace.cost.materials.bounds[1],
    input$replace.cost.materials.ev,
    input$replace.cost.materials.bounds[2]
  )*1000})
  
  new.cost.labor <- reactive({c(
    input$replace.cost.labor.bounds[1],
    input$replace.cost.labor.ev,
    input$replace.cost.labor.bounds[2]
  )*1000})
  
  new.cost.outage <- reactive({c(
    input$replace.cost.outage.bounds[1],
    input$replace.cost.outage.ev,
    input$replace.cost.outage.bounds[2]
  )*1000})
  
  new.life <- reactive({c(
    input$replace.life.bounds[1],
    input$replace.life.ev,
    input$replace.life.bounds[2]
  )})

```


```{r sim_df}



sim.pert.all <- reactive(
  {
    sim.pert <- sapply(
        list(
          refurb.cost.materials(), refurb.cost.labor(), refurb.cost.outage(),
          refurb.life(), new.cost.materials(), new.cost.labor(), new.cost.outage(),
          new.life(), sunk.cost.labor(), sunk.cost.outage()
        ),
        \(x){ fn_vector_to_dist(n(), x, rpert)}
      ) %>%
        as_tibble() %>%
        rename_all(~ c(
          "refurb.cost.mats", "refurb.cost.labor", "refurb.cost.outage", "refurb.L",
          "new.cost.mats", "new.cost.labor", "new.cost.outage", "new.L",
          "coincidental.cost.labor", "coincidental.cost.outage"
        )) %>% 
        mutate(across(-contains("L", ignore.case = F), \(x){x * n.units()}))
  
    cost.refurb.pert <- sim.pert %>%
      mutate(rate.discount = rate.discount()) %>% 
      pmap_dbl(., .f = fn_cost.refurb)
  
  
    cost.replace.pert <- sim.pert %>%
      select(contains("new") | contains("coin")) %>%
      mutate(rate.discount = rate.discount()) %>% 
      pmap_dbl(., .f = fn_cost.replace)
  
    sim.pert.all <- cbind(sim.pert, cost.refurb.pert, cost.replace.pert) %>%
      mutate(
        cost.net = cost.refurb.pert - cost.replace.pert,
        optimal.choice = ifelse(cost.net >= 0, "replace", "refurb")
      )
  
    return(sim.pert.all)

  }) %>% 
  bindEvent(input$run.simulation)


# Probabilities
prob <- reactive({
  fn_fit.logit(simulation = sim.pert.all(), rate.discount = rate.discount())
})

# Breakeven
refurb.L.breakeven <- reactive({
  fn_get.breakeven(sim.pert.all()$refurb.L, prob(), .5)
})

```



Simulation Results
======================================================================

Column
-----------------------------------------------------------------------

```{r}

# Cost Min, Max
cost.refurb.min <- reactive({
  min(sim.pert.all()$cost.refurb.pert)
})

cost.refurb.max <- reactive({
  max(sim.pert.all()$cost.refurb.pert)
})

cost.replace.min <- reactive({
  min(sim.pert.all()$cost.replace.pert)
})

cost.replace.max <- reactive({
  max(sim.pert.all()$cost.replace.pert)
})

cost.min <- reactive({
  min(cost.refurb.min(), cost.replace.min())
})

cost.max <- reactive({
  max(cost.refurb.max(), cost.replace.max())
})



```


### Option 1:  PV Unit Cost to Refurbish Now and Then Replace at End of Life 

```{r chart_cost.refurb}

# renderTable({
#   sim.pert.all() %>% colnames()
# })
renderPlot({
  sim.pert.all()$cost.refurb.pert %>%
    fn_chart.shaded.density() +
    scale_x_continuous(
      # "PV Cost", 
      labels = scales::label_dollar(),
      limits = c(cost.min(), cost.max())
    ) +
    theme(
      axis.title = element_blank()
    )
})

```

### Option 2:  PV Unit Cost to Replace Now

```{r}

renderPlot({
  sim.pert.all()$cost.replace.pert %>%
    fn_chart.shaded.density() +
    scale_x_continuous(
      # "PV Cost", 
      labels = scales::label_dollar(),
      limits = c(cost.min(), cost.max())
    ) +
    theme(
      axis.title = element_blank()
    )
  
  
})
```


### Net Difference: PV Savings [Cost] by doing Option 2 

```{r}
 renderPlot({
   # fn_chart.cost.net(sim.pert.all()) +
   #   theme(
   #     plot.title = element_blank()
   #   )
   
   fn_chart.shaded.density(sim.pert.all()$cost.net) +
    annotate(
      "text", x = -100000, y = 0, label = "← Refurbish is optimal", size = 3,
      hjust = 1, vjust = 1
    ) +
    annotate(
      "text", x = 100000, y = 0, label = "Replace is optimal →", size = 3,
      hjust = 0, vjust = 1
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    scale_x_continuous(
      "NPV of doing Option 2", 
      labels = scales::label_dollar()
    ) +
    theme(
      plot.title = element_blank()
    )
 })

```



Column {data-width=140}
-----------------------------------------------------------------------

```{r}

tbl.summary <- reactive({
  sim.pert.all() %>% 
  select(-optimal.choice) %>%
    mutate(
      `Refurbished Labor Cost` = refurb.cost.labor,# - coincidental.cost.labor,
      `Refurbished Outage Cost` = refurb.cost.outage,# - coincidental.cost.outage,
      `Replace Labor Cost` = new.cost.labor,# - coincidental.cost.labor,
      `Replace Outage Cost` = new.cost.outage,# - coincidental.cost.outage,
      
      .keep = "unused"
    ) %>% 
    relocate(starts_with("refurb"), starts_with("new"), starts_with("Replace"), contains("cost")) %>% 
    rename(
      `Refurbished Materials Cost` = refurb.cost.mats, 
      `Replace Materials Cost` = new.cost.mats, 
      `Refurbished Unit Life` = refurb.L,
      `PV Cost - Refurbished` = cost.refurb.pert,
      `PV Cost - Replace` = cost.replace.pert,
      `NPV Cost` = cost.net
    ) %>% 
    select(-contains("coin"), -new.L) %>% 
    summarize(
      across(everything(), .fns = mean)
    ) %>% 
    pivot_longer(cols = everything(), names_to = "Variable", values_to = "Mean") %>% 
    mutate(
      Mean = label_comma()(Mean)
    )
})

renderUI({
  tbl.summary() %>% 
    kbl(align = c("l", "r")) %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "center") %>% 
    HTML()
})

```

```{r}

choice.proportions <- reactive({
  sim.pert.all() %>% 
    count(optimal.choice) %>% 
    mutate(
      percent = n / sum(n)
    )
})

best.replace.prop <- reactive({
  choice.proportions()[choice.proportions()$optimal.choice == "replace", "percent"]
})

best.refurb.prop <- reactive({
  choice.proportions()[choice.proportions()$optimal.choice == "refurb", "percent"]
})

best.sentence <- reactive({
  if(best.replace.prop() >= .5){
    paste0(
      label_percent()(best.replace.prop()), " of cases result in replacement being the better choice.",
      " The other ", label_percent()(best.refurb.prop()), " of cases have refurbishment being better."
    )
  } else{
    paste0(
      label_percent()(best.refurb.prop()), " of cases result in refurbishment being the better choice.",
      " The other ", label_percent()(best.replace.prop()), " of cases have replacement being better."
    )
  }
  
})

# suggestion <- reactive({
#   if(best.replace.prop() >= .6){
#     paste("Recommendation under current parameters:", "Replace", sep = "\n\t")
#   } else if(best.refurb.prop() >= .6){
#     paste0("Recommendation under current parameters:\n\tRefurbish")
#   } else{
#     "Replace & refurbish both result in about the same cost."
#   }
# })


```

> `r renderText({best.sentence()})` 

Marginal Plots
======================================================================

Column {data-width=400, .tabset}
-----------------------------------------------------------------------


```{r include=FALSE}


tbl.refurb.L <- reactive({
  sim.pert.all() %>% 
    as_tibble() %>% 
    mutate(
        refurb.L = round(refurb.L)
      ) %>% 
      group_by(refurb.L) %>% 
      summarise(
        # n = n(),
        across(c(cost.refurb.pert, cost.replace.pert, cost.net), mean)
      ) %>% 
    filter(between(refurb.L, refurb.L.breakeven() - 5, refurb.L.breakeven() + 5)) %>% 
    mutate(across(c(cost.refurb.pert, cost.replace.pert, cost.net), \(x){label_dollar(accuracy = .01, scale = 1/1000000, suffix = "M")(x)})) %>% 
    rename_with(~c("Refurbished Life", "Avg Refurb Cost", "Avg Replace Cost", "Avg Diff")) # , "Modeled Refurb Cost"
})

```


### Refurbished Wicket Gate Life

```{r chart_scatter}
#### Scatterplot of Project Net Present Value to Refurbished Wicket Gate life

renderPlot({
  grid.arrange(
    (fn_chart.marginal.scatter(sim.pert.all(), "refurb.L", x.label = "Life of Refurbished Wicket Gate") + 
      annotate(
        geom = "table", x = Inf, y = Inf, 
        label = list(tbl.refurb.L()), 
        vjust = 1, size = 4
      )) %>% 
      ggMarginal(., type = "histogram", margins = "x", size = 10),
    fn_chart.marginal.frequency(sim.pert.all(), "refurb.L", x.label = "Life of Refurbished Wicket Gate")
  )
})

    
```


### Refurbished Material Cost

```{r}
#### Scatterplot of Project Net Present Value to Refurbished Wicket Gate life

renderPlot({
  grid.arrange(
    fn_chart.marginal.scatter(
      sim.pert.all(), "refurb.cost.mats", alpha.var = "refurb.L", x.label = "Material Cost to Refurbish"
    ),
    fn_chart.marginal.frequency(sim.pert.all(), "refurb.cost.mats", x.label = "Material Cost to Refurbish")
  )
})

    
```


### Replace Material Cost

```{r}
#### Scatterplot of Project Net Present Value to Refurbished Wicket Gate life

renderPlot({
  grid.arrange(
    fn_chart.marginal.scatter(
      sim.pert.all(), "new.cost.mats", alpha.var = "refurb.L", x.label = "Material Cost to Replace"
    ) %>% 
      ggMarginal(., type = "histogram", margins = "x", size = 10),
    fn_chart.marginal.frequency(sim.pert.all(), "new.cost.mats", x.label = "Material Cost to Replace")
  )
})

    
```



### Future Outage Cost

```{r}
#### Scatterplot of Project Net Present Value to Refurbished Wicket Gate life

renderPlot({
  grid.arrange(
    fn_chart.marginal.scatter(
      sim.pert.all(), "new.cost.outage", alpha.var = "refurb.L", x.label = "Future Outage Cost"
    ) %>% 
      ggMarginal(., type = "histogram", margins = "x", size = 10),
    fn_chart.marginal.frequency(sim.pert.all(), "new.cost.outage", x.label = "Future Outage Cost")
  )
})

    
```


### Future Labor Cost

```{r}
#### Scatterplot of Project Net Present Value to Refurbished Wicket Gate life

renderPlot({
  grid.arrange(
    fn_chart.marginal.scatter(
      sim.pert.all(), "new.cost.labor", alpha.var = "refurb.L", x.label = "Future Labor Cost"
    ),
    fn_chart.marginal.frequency(sim.pert.all(), "new.cost.labor", x.label = "Future Labor Cost")
  )
})

    
```



Probabilistic Modeling
======================================================================

```{r eval=FALSE, include=FALSE}



```

Column {.tabset}
-----------------------------------------------------------------------



### Refurbished Wicket Gate Life

```{r}

renderPlot({
  (fn_chart.logit(
    sim.pert.all(), prob(), quantile.vec = c(.1,.25,.5,.75, .9), x.var = "refurb.L"
  ) + xlab("Life of Refurbished Wicket Gate")) %>%
    ggMarginal(., type = "histogram", margins = "both", size = 10)
})


```


### Refurbished Material Cost


```{r}


renderPlot({
  (fn_chart.logit(
    sim.pert.all(), prob(), quantile.vec = c(.1,.25,.5,.75, .9), 
    x.var = "refurb.cost.mats", 
    fn_format = label_dollar(
      accuracy = .01, scale = 1/1000000, suffix = "M"
    )
  ) +
    scale_x_continuous(
      labels = label_dollar()
      # expand = expansion(mult = .1)
    ) +
    theme(
      legend.position = c(.75,.1)
    ) + 
      xlab("Material Cost to Refurbish")) %>% 
    ggMarginal(., type = "histogram", margins = "both", size = 10)
})


```




### Replace Material Cost

```{r}


renderPlot({
  (fn_chart.logit(
    sim.pert.all(), prob(), quantile.vec = c(.1,.25,.5,.75, .9), 
    x.var = "new.cost.mats", 
    fn_format = label_dollar(
      accuracy = .01, scale = 1/1000000, suffix = "M"
    )
  ) +
    scale_x_continuous(
      labels = label_dollar()
      # expand = expansion(mult = .15)
    ) + 
      xlab("Material Cost to Replace") +
    theme(
      legend.position = c(.1,.2)
    )) %>% 
    ggMarginal(., type = "histogram", margins = "both", size = 10)
})


```

### Future Outage Cost

```{r}


renderPlot({
  (fn_chart.logit(
    sim.pert.all(), prob(), quantile.vec = c(.1,.25,.5,.75, .9), 
    x.var = "new.cost.outage", 
    fn_format = label_dollar(
      accuracy = .01, scale = 1/1000000, suffix = "M"
    )
  ) +
    scale_x_continuous(
      labels = label_dollar()
      # expand = expansion(mult = .15)
    ) + xlab("Future Outage Cost") +
    theme(
      legend.position = c(.2,.2)
    )) %>% 
    ggMarginal(., type = "histogram", margins = "both", size = 10)
})


```



### Future Labor Cost

```{r}


renderPlot({
  (fn_chart.logit(
    sim.pert.all(), prob(), quantile.vec = c(.1,.25,.5,.75, .9), 
    x.var = "new.cost.labor", 
    fn_format = label_dollar(
      accuracy = .01, scale = 1/1000000, suffix = "M"
    )
  ) +
    scale_x_continuous(
      labels = label_dollar()
      # expand = expansion(mult = .15)
    ) + xlab("Future Labor Cost") +
    theme(
      legend.position = c(.2,.2)
    )) %>% 
    ggMarginal(., type = "histogram", margins = "both", size = 10)
})


```


Column {data-width=140}
-----------------------------------------------------------------------



> These charts and probabilities are modeled using logistic regression. The *Estimated Probability* is the predicted chance that replacement is the better choice for a given observation. The color of each observation identifies the true optimal decision. The curve reflects the average probability given the corresponding variable on the X axis.

> The *breakeven point*, where there is an equal probability between replacement versus refurbishment being the better choice, is identified where the logistic curve is equal to 50%.


Documentation 
======================================================================

Column 
-----------------------------------------------------------------------

### Instructions 

1. The left pane contains the inputs to the model and actions. 
  - The scales adjust to specify the lower and upper bounds for the input.
  - The text box contains the expected value.
2. Hit the button "Run simulation" to begin.
3. Navigate the pages along the top to view different charts and tables.
4. The tabs *Marginal Plots* and *Probabilistic Modeling* both contain tabs of different variables.


### Overview 
- The PERT distribution is used to simulate the input values.
  - This is a transformation of the Beta distribution and is common to use for project management simulations. 
- The costs of both options are calculated for each sample of the simulation. The tables and charts are generated from this simulated data.
- Because each of these options compare different durations (*option 1 is the life of refurbished wicket gate + life of new wicket gate / option 2 is only life of new wicket gate*), a costs-in-perpetuity adjustment is made to equalize these durations.
  - The material, outage, and labor costs for a new wicket gate are assumed to occur every 100 years in perpetuity. These future costs are discounted to the present and added to both options, normalizing the durations between both.
    - These costs far in the future are discounted tremendously and only add a small amount to the total costs. 
      - Example: $1M cost occurring every 100 years starting in 100 years has a PV of $12,409 at a 4.5% discount rate.
  - This differs from the Excel model. The model in Excel uses straight-line depreciation to equalize the durations. Both models provide consistent results with one another although some differences in the PV costs will be present.
  - The difference in the PV costs will be proportional to the size of the costs and does not change the results.
  

### Simulation Results

- This page shows the overall results of the simulation.
- The distributions are the calculated PV costs for each observation in the simulation.
- The bottom distribution is the difference of Option 2 costs to Option 1 costs for each observation.
  - Positive values are savings by switching to Option 2.
  - Negative values are added costs by switching to Option 2.

### Marginal Plots

- This page shows the relation of the Net Cost (Cost of Option 2 - Cost of Option 1) to several variables: Refurbished Wicket Gate Life, Refurbished Material cost, Replace Material Cost, Future Outage Cost, and Future Labor Cost.
- The bottom chart shows the frequency plots for when Replace/Refurbish is the optimal choice. 
  - Where the two lines intersect is the breakeven point, the point where there is a 50-50 chance of one option over the other.
  

### Probabilititic Modeling
- This page fits a logistic regression model to the data.
- The logistic curve gives the probability that replacement is the optimal choice for each value on the X-axis.
  - I.e. For the life of refurbished wicket gate at 30 years, the logistic curve is at ~95%, meaning there is a 95% probability that at that refurbished life that replacement is the better option.
- Shifts to the other parameters will result in a different logistic curve.
  - I.e. With a $1M increase to the refurbish material cost, a greater refurbished wicket gate life would be needed to maintain it being the optimal choice. 
- Tips:
  - To reduce the error margin of the logistic curve, increase the sample size of the simulation or widen the bounds of that input. Either of these actions will decrease the *standard error* of the model and provide a better logistic fit.